\cvsection{Education}
\begin{cventries}

	\cventry
	{IBM} % Institution
	{Preparation for CompTIA A+ Certification} % Degree
	{Coursera} % Location
	{Jan. 2025} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
		\item{Completed IBM's CompTIA A+ prep course covering hardware, software, networking, troubleshooting, and security for the 220-1101 \& 220-1102.}
		\end{cvitems}
	}

	\cventry
	{Google} % Institution
	{AI Essentials Certificate} % Degree
	{Coursera} % Location
	{Oct. 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
		\item{Integrated AI into generative workflows with responsible AI principles, engineering \& optimizing prompts, and experience with 10+ AI tools.}
		\end{cvitems}
	}

	\cventry
	{Google} % Institution
	{IT Support Professional Certificate} % Degree
	{Coursera} % Location
	{Sep. 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
		\item{Mastered IT foundations such as networking, operating systems, system administration, encryption, security, and permissions.}
		\end{cvitems}
	}

	\cventry
	{Clovis Community College} % Institution
	{A.S. in Information Technology} % Degree
	{Clovis, California} % Location
	{Dec. 2023} % Date(s)
	% {Aug. 2017 - Dec. 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
		\item{Programming Concepts and Methodology, Computer Architecture, Discrete Mathematics for Computer Science, \& Data Structures Visualization}
		\end{cvitems}
	}

	\cventry
	  {Liberty High School} % Institution
	  {High School Diploma} % Degree
	  {Madera, California} % Location
	  {Mar. 2017} % Date(s)
	  {
	    \begin{cvitems} % Description(s) bullet points
	\item {Architecture, Construction, \& Engineering (ACE), Regional Occupational Programs (ROP) such as ROP Robotics \& ROP Digital Media}
	    \end{cvitems}
	  }
\end{cventries}
