%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cloud Systems Administrator} % Job title
    {OurPetDr} % Organization
    {Remote, Bakersfield CA} % Location
    {Jul. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {Developed and deployed a virtual instance for the operations of a global Veterinarian company. To be compliant with PCI data security standards I had to register a FQDN, install TLS/SSL certs, and follow basic secutity measures such as disabling weak ciphers, disabling root access from the web, and banning brute-force ssh attempts. }
		  \item {Significantly sped up the invoicing and subscriptions by implementing a pipeline to automate the tedious process of assigning pet owners with Veterinarians by intercepting webhooks send from the Stripe API.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Annotation Technician} % Job title
    {Outlier AI} % Organization
    {Remote, Oakland CA} % Location
    {Oct. 2023 - Mar. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {Compared AI code execution and output for safety, accuracy, and fulfillment. Used Google Data Compute to complete data entry tasks like rating and explaining AI model performance. Analyzed autonomous vehicle data to identify pedestrians, vehicles,authorities, and other hazards with LiDAR. Trained an AI to detect and distinguish veins, arteries, stents, and blood clots in the human body by annotating catheter footage frame by frame.}
		  \item {Used Slack to develop leadership through communication and troubleshooting with 500K community members. As the community grew rapidly, issues and questions went overlooked. I enjoyed helping team members struggling with AI projects and conversing as a team to decide project outcomes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sales Associate} % Job title
    {Costco Wholesale} % Organization
    {Fresno, California} % Location
    {Nov. 2017 - Mar. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  \item {Sales required technical knowledge about our entire device inventory. I would help members with personal device issues, decide between tech products, track terminal inventory, track member information, place \& answer phone calls, operate pallet jacks to stock store inventory, cashier and count money,audit jewelry, and manage the photo center.}
		  \item {Learned that enthusiasm and communication are needed to work efficiently with others, and customer experience requires listening and a positive attitude. Because of my work ethic, I was the first person relied on to complete special projects.} 
	  \end{cvitems}
	 }
%---------------------------------------------------------
\end{cventries}
